How to use replication assignments for teaching integrity in empirical archaeology

### 2019-06-23 analysis/paper/paper.Rmd
add Wessa

The longer term practical benefits include cultivating a reproducibility routine for students to develop a natural habit of organising their code and data for future work so another person can use it to reproduce their results. Benefits also include developing professionalism among students: by working through the steps of an analysis students gain an understanding of what kinds of decisions in all steps of an analysis are acceptable (Janz 2018). Although the small scale of our assignment did not offer the potential for students to publish new findings from replication, we anticipate this may be a benefit for archaeology students participating in more extensive replication assignments.

The challenges of requiring students to do replication assignments are similar to those faced in many types of archaeology classes with quantitative skills at their core. In our case, the absence of a prerequisite and the high variability of statistical and programming skills meant that some students needed a lot more support than others. This may make replication assignments impractical where instructor-student contact hours are limited. In addition to time, the instructor needs to have a high skill level in quantitative methods to guide students in their engagement with the literature. The instructor will also benefit from a high tolerance for helping students to solve coding problems. To mitigate this in the future we will add a step of student peer review to distribute the feedback task beyond the instructor and give students an opportunity to get assistance from each other more formally.

>>>>

The longer term practical benefits include cultivating a reproducibility routine for students to develop a natural habit of organising their code and data for future work so another person can use it to reproduce their results. Benefits also include developing professionalism among students: by working through the steps of an analysis students gain an understanding of what kinds of decisions in all steps of an analysis are acceptable [@janz2016bringing]. Although the small scale of our assignment did not offer the potential for students to publish new findings from replication, we anticipate this may be a benefit for archaeology students participating in more extensive replication assignments.

The challenges of requiring students to do replication assignments are similar to those faced in many types of archaeology classes with quantitative skills at their core. In our case, the absence of a prerequisite and the high variability of statistical and programming skills meant that some students needed a lot more support than others. This may make replication assignments impractical where instructor-student contact hours are limited. In addition to time, the instructor needs to have a high skill level in quantitative methods to guide students in their engagement with the literature. The instructor will also benefit from a high tolerance for helping students to solve coding problems. To mitigate this in the future we will add a step of student peer review [@wessa2009reproducible] to distribute the feedback task beyond the instructor and give students an opportunity to get assistance from each other more formally.
